Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-06-14 unimodular-covers.tex
drawn attempt of counter-example

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}

@@

@@

%Further, we observe that both vertices of $f_1$ (or $f_2$) cannot lie strictly above the line through $q_1$ and $q_2$, else the strip would contain a lattice point. 
\end{proof}
]
\begin{proof}[Proof of \Cref{thm:cayley}]
Consider any lattice triangulation $\T$ of $\cayley(P,Q)$, or equivalently a mixed subdivision of $P+Q$. Observe that any simplex in $T$ has vertices in $Px\{0\}$ or in $Q \times \{1\}$, since $\cayley(P,Q)$ lies between two consecutive lattice hyperplanes $\{x_3=0\}$ and $\{x_3=1\}$. Thus simplices in $\T$ are of three types; they can , or have three vertices in $P$ and one in $Q$ (type $(3,1)$), have one vertex in $P$ and three in $Q$ (type $(1,3)$) or have two vertices in $P$ and two in $Q$ (type $(2,2)$). \giulia{is it usually denoted by dimension or cardinality? that is, (2,0) or (3,1)?} A triangulation of a simplex of type $(3,1)$ (resp $(1,3)$) is obtained by simply unimodularly triangulating the triangular face lying in $P$ (resp $Q$) and coning over the vertex in $Q$ (resp $P$). This leaves simplices of type $(2,2)$. In the mixed subdivision of $P+Q$ corresponding to $T$, these are mixed cells, that is parallelograms with one edge in $P$ and one in $Q$ \giulia{how imprecise can I be without being confusing?}.

>>>>

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}

@@

\begin{figure}[htb]
  \centering
\begin{tikzpicture}[mynode/.style={circle, inner sep=1.5pt, fill=red}, scale =
  .8]
%coordinate axes
   \tkzInit[xmax=3.5,ymax=3.5,xmin=-3.5,ymin=-3.5]
%        \tkzLabelX[orig=false,label options={font=\tiny}]
%        \tkzLabelY[orig=false,label options={font=\tiny}]
        \tkzGrid
%       \tkzDrawX
%       \tkzDrawY

%hexagon
  \node[mynode] (A) at (0,-1) {}; 
%  \node[mynode] (B) at (1,1) {};  
  \node[mynode] (C) at (2,3) {};  
  \node[mynode] (D) at (0,1) {};  
%  \node[mynode] (E) at (-1,-1) {};  
  \node[mynode] (F) at (-2,-3) {};

%other points
%  \node[mynode] () at (0,-1) {};

  \draw[black] (A) -- (C) -- (D) -- (F) -- (A);
  \draw[black, thick] (A) -- (D);
\end{tikzpicture}
%
\begin{tikzpicture}[mynode/.style={circle, inner sep=1.5pt, fill=red}, scale =
  .8]
%coordinate axes
   \tkzInit[xmax=3.5,ymax=3.5,xmin=-3.5,ymin=-3.5]
%        \tkzLabelX[orig=false,label options={font=\tiny}]
%        \tkzLabelY[orig=false,label options={font=\tiny}]
        \tkzGrid
%        \tkzDrawX
%        \tkzDrawY

%hexagon
  \node[mynode] (A) at (1,0) {}; 
  \node[mynode] (B) at (2,1) {};  
  \node[mynode] (C) at (3,3) {};  
  \node[mynode] (D) at (-1,0) {};  
  \node[mynode] (E) at (-2,-1) {};  
  \node[mynode] (F) at (-3,-3) {};

  \draw[black] (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- (A);
  \draw[black, thick] (A) -- (D);
\end{tikzpicture}

\centerline{\hfill $P$ \hfill\hfill $Q$ \hfill}

\caption{Partial counter-example to \Cref{lemma:cayley}. It is not a counter-example because (a) the edges $p_1p_2$ and $q_1q_2$ are not primitive and (b) the origin is a lattice point in the interior of both bands (but it is the only one). 
%
With respect to the lattice of index two it is not a counter-example either, because two vertices of $Q$ are not in that lattice.
}
\label{fig:width3}
\end{figure}

@@

%Further, we observe that both vertices of $f_1$ (or $f_2$) cannot lie strictly above the line through $q_1$ and $q_2$, else the strip would contain a lattice point. 
\end{proof}

\begin{proof}[Proof of \Cref{thm:cayley}]
Consider any lattice triangulation $\T$ of $\cayley(P,Q)$, or equivalently a mixed subdivision of $P+Q$. Observe that any simplex in $T$ has vertices in $Px\{0\}$ or in $Q \times \{1\}$, since $\cayley(P,Q)$ lies between two consecutive lattice hyperplanes $\{x_3=0\}$ and $\{x_3=1\}$. Thus simplices in $\T$ are of three types; they can , or have three vertices in $P$ and one in $Q$ (type $(3,1)$), have one vertex in $P$ and three in $Q$ (type $(1,3)$) or have two vertices in $P$ and two in $Q$ (type $(2,2)$). \giulia{is it usually denoted by dimension or cardinality? that is, (2,0) or (3,1)?} A triangulation of a simplex of type $(3,1)$ (resp $(1,3)$) is obtained by simply unimodularly triangulating the triangular face lying in $P$ (resp $Q$) and coning over the vertex in $Q$ (resp $P$). This leaves simplices of type $(2,2)$. In the mixed subdivision of $P+Q$ corresponding to $T$, these are mixed cells, that is parallelograms with one edge in $P$ and one in $Q$ \giulia{how imprecise can I be without being confusing?}.
